Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-06-23 Report/decomposition_solutions.tex
updated revision 2 with ADMM proof and strict monotonicity

Let us consider the convex subproblem with the fixed receive beamformers \me{\mvec{w}{l,k,n}} presented in \eqref{eqn-9} based on the Taylor series approximation for the nonconvex constraint. The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well. Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
\begin{subeqnarray} \label{eqn-decent-1} \allowdisplaybreaks
&\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}}& \quad \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \slabel{eqn-decent-1a} \\
&\text{subject to}& \quad \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber
\end{subeqnarray}
where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.

@@

The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} to a parallel iterative subproblems coordinated by either primal or \acl{DD} update. The coupling variables are updated in each iteration by exchanging limited information among the subproblems. Before proceeding further, let \me{\bar{\mbfa{\zeta}}_b} be the vector formed by stacking interference terms \eqref{inter_exp} from the neighboring \acp{BS} to the users of \ac{BS} \me{b} and \me{\hat{\mbfa{\zeta}}_{b}} be the stacked interference terms caused by \ac{BS} \me{b} to all users in the neighboring \acp{BS} \me{\bar{\mc{B}}_b}, represented as
\begin{subeqnarray}
\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,k,n,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{l,k,n,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran, \forall k \in \mc{U}_{b} \\
\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,\bar{\mc{U}}_b(1),n,b}, {\zeta}_{l,\bar{\mc{U}}_b(2),n,b}, \dotsc, {\zeta}_{l,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),n,b} \right]^\tran.
\end{subeqnarray}
Let us define the vector \me{\mbfa{\zeta}_b}, formed by stacking the interference terms corresponding to the \ac{BS} \me{b} as
\begin{equation}
\mbfa{\zeta}_{b} = \left [\hat{\mbfa{\zeta}}_{b}^\tran, \bar{\mbfa{\zeta}}_{b}^\tran \right ]^\tran. \label{if_vector}
\end{equation}
Since the decentralization solution is an iterative procedure, we represent the \me{\ith{i}} iteration index as \me{x^{(i)}}. Let \me{\mbfa{\zeta}_{b}(b_k)} denote the interference terms corresponding to \ac{BS} \me{b_k} in \ac{BS} \me{b} as
\begin{equation}
\mbfa{\zeta}_{b}(b_k) = \left [ {\zeta}_{l,\mc{U}_b(1),n,b_k},\dotsc, {\zeta}_{l,\mc{U}_b(|\mc{U}_b|),n,b_k} \right].
\end{equation}

>>>>

Let us consider the convex subproblem with the fixed receive beamformers \me{\mvec{w}{l,k,n}} presented in \eqref{eqn-9} based on the Taylor series approximation for the nonconvex constraint. The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well. Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
\begin{IEEEeqnarray}{rCl} \label{eqn-decent-1} \allowdisplaybreaks  \neqsub
&\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}}& \quad \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
&\text{subject to}& \quad \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.

@@

The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} to a parallel iterative subproblems coordinated by either primal or \acl{DD} update. The coupling variables are updated in each iteration by exchanging limited information among the subproblems. Before proceeding further, let \me{\bar{\mbfa{\zeta}}_b} be the vector formed by stacking interference terms \eqref{inter_exp} from the neighboring \acp{BS} to the users of \ac{BS} \me{b} and \me{\hat{\mbfa{\zeta}}_{b}} be the stacked interference terms caused by \ac{BS} \me{b} to all users in the neighboring \acp{BS} \me{\bar{\mc{B}}_b}, represented as
\begin{IEEEeqnarray}{rCl} \neqsub
\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,k,n,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{l,k,n,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran, \forall k \in \mc{U}_{b} \eqsub \\
\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,\bar{\mc{U}}_b(1),n,b}, {\zeta}_{l,\bar{\mc{U}}_b(2),n,b}, \dotsc, {\zeta}_{l,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),n,b} \right]^\tran. \eqsub
\end{IEEEeqnarray}
Let us define the vector \me{\mbfa{\zeta}_b}, formed by stacking the interference terms corresponding to the \ac{BS} \me{b} as
\begin{equation}
\mbfa{\zeta}_{b} = \left [\hat{\mbfa{\zeta}}_{b}^\tran, \bar{\mbfa{\zeta}}_{b}^\tran \right ]^\tran. \label{if_vector}
\end{equation}
Since the decentralization solution is an iterative procedure, we represent the \me{\ith{i}} iteration index as \me{x^{(i)}}. Let \me{\mbfa{\zeta}_{b}(b_k)} denote the interference terms corresponding to \ac{BS} \me{b_k} in \ac{BS} \me{b} as
\begin{equation}
\mbfa{\zeta}_{b}(b_k) = \left [ {\zeta}_{l,\mc{U}_b(1),n,b_k},\dotsc, {\zeta}_{l,\mc{U}_b(|\mc{U}_b|),n,b_k} \right].
\end{equation}

### 2015-06-23 Report/dual_approach.tex
updated revision 2 with ADMM proof and strict monotonicity

The \ac{ADMM} approach is used to decouple the precoder design across multiple \acp{BS} to solve the convex problem in \eqref{eqn-decent-1}. The \ac{ADMM} is preferred over the \ac{DD} approach in \cite{tolli2011decentralized} for its robustness and improved convergence behavior \cite{boyd2011distributed}. In contrast to the \acl{PD}, the \ac{ADMM} approach relaxes the interference constraints by including in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}. Similar approach for the precoder design in the minimum power context is considered in \cite{admm_robust}.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
				\me{j = j + 1}\;
			}
			precoded downlink pilot transmission with \me{\mvec{m}{l,k,n}}\;
			update \me{\mvec{w}{l,k,n}} to all \acp{BS} in \me{\mc{B}} using precoded uplink pilots \cite{komulainen2013effective}\;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}

Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{i}} iteration as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}\allowdisplaybreaks
\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} &\quad& \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
\text{subject to} &\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\quad&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
&\quad& \sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
&\quad& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}
}{\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks
&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}}
where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{i}} iteration as
\begin{equation} \label{const-admm1}
\mbfa{\zeta}_b = \mbfa{\zeta}^{(i)}_b.
\end{equation}

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual vector for the next iteration is updated by using the subgradient search to maximize the dual objective as
\begin{equation}
\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right )
\label{dual-sg-update}
\end{equation}
where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model under consideration. The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}. For our simulation models, we consider step size parameter \me{\rho=2}. The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates. The distributed precoder design using the \ac{ADMM} approach is shown in Algorithm \ref{algo-3}. The convergence analysis of the distributed algorithms are discussed in Appendix \ref{sec-dist-conv}.

>>>>

The \ac{ADMM} approach is used to decouple the precoder design across multiple \acp{BS} to solve the convex problem in \eqref{eqn-decent-1}. The \ac{ADMM} is preferred over the \ac{DD} approach in \cite{tolli2011decentralized} for its robustness and improved convergence behavior \cite{boyd2011distributed}. In contrast to the \acl{PD}, the \ac{ADMM} approach relaxes the interference constraints by including in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}. Similar approach for the precoder design in the minimum power context is considered in \cite{admm_robust}.

Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{i}} iteration as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} &\quad& \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
\text{subject to} &\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\quad&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
&\quad& \sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
&\quad& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}
}{\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}}
where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{i}} iteration as
\begin{equation} \label{const-admm1}
\mbfa{\zeta}_b = \mbfa{\zeta}^{(i)}_b.
\end{equation}

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual vector for the next iteration is updated by using the subgradient search to maximize the dual objective as
\begin{equation}
\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right )
\label{dual-sg-update}
\end{equation}
where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model under consideration. The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}. For our simulation models, we consider step size parameter \me{\rho=2}. The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates. The distributed precoder design using the \ac{ADMM} approach is shown in Algorithm \ref{algo-3}. The convergence analysis of the distributed algorithms are discussed in Appendix \ref{sec-dist-conv}.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
				\me{j = j + 1}\;
			}
			precoded downlink pilot transmission with \me{\mvec{m}{l,k,n}}\;
			update \me{\mvec{w}{l,k,n}} to all \acp{BS} in \me{\mc{B}} using precoded uplink pilots \cite{komulainen2013effective}\;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$, \me{j=0} \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}

### 2015-06-23 Report/ieee_journal.tex
updated revision 2 with ADMM proof and strict monotonicity

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage{graphicx,epstopdf}
\usepackage[ruled]{algorithm2e}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
\usepackage{multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools,url,subeqnarray}

@@

\subsection{Queue Weighted Sum Rate Maximization (\acs{Q-WSRM}) Formulation} \label{sec-3.1} %\acused{Q-WSRM}
\input{joint_wsrm_formulation}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage{graphicx,epstopdf}
\usepackage[ruled]{algorithm2e}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases}

@@

\subsection{Queue Weighted Sum Rate Maximization (\acs{Q-WSRM})} \label{sec-3.1} %\acused{Q-WSRM}
\input{joint_wsrm_formulation}

### 2015-06-23 Report/introduction.tex
updated revision 2 with ADMM proof and strict monotonicity

The problem of precoder design for the \ac{MIMO} \ac{IBC} system can be solved either by using a centralized controller or by using decentralized algorithms, where each \ac{BS} handles the corresponding subproblem independently with the limited information exchange with other \acp{BS} via back-haul. The distributed approaches are usually based on the primal, or dual decompositions or the \ac{ADMM}, which has been discussed in \cite{palomar2006tutorial,boyd2011distributed}. In the  primal decomposition, the so-called coupling interference variables are fixed for the subproblem at each \ac{BS} to find the optimal precoders. The fixed interference is then updated by using the subgradient method as discussed in \cite{pennanen2011decentralized}. The dual and the \ac{ADMM} approaches control the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.

@@

The rest of the paper is organized as follows. In Section \ref{sec-2-3.2}, we introduce the system model and the problem formulation for the queue minimizing precoder design. The existing and the proposed centralized precoder designs are presented in Section \ref{sec-3}. The distributed solutions are provided in Section \ref{sec-4} followed by the simulation results in Section \ref{sec-5}. Conclusions are drawn in Section \ref{sec-6}.

>>>>

The problem of precoder design for the \ac{MIMO} \ac{IBC} system can be solved either by using a centralized controller or by using decentralized algorithms, where each \ac{BS} handles the corresponding subproblem independently with the limited information exchange with other \acp{BS} via back-haul. The distributed approaches are usually based on the primal, or dual decompositions or the \ac{ADMM}, which has been discussed in \cite{palomar2006tutorial,boyd2011distributed}. In the  primal decomposition, the so-called coupling interference variables are fixed for the subproblem at each \ac{BS} to find the optimal precoders. The fixed interference is then updated using the subgradients as discussed in \cite{pennanen2011decentralized}. The dual and the \ac{ADMM} approaches control the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.

@@

The rest of the paper is organized as follows. Section \ref{sec-2-3.2} introduces the system model and the problem formulation for the proposed design. The existing and the proposed centralized designs are presented in Section \ref{sec-3}. The distributed solutions are provided in Section \ref{sec-4} followed by the simulation results in Section \ref{sec-5}. Conclusions are drawn in Section \ref{sec-6}.
